---
title: "collaborator-analysis"
author: Harshmeet Singh
format: html
---

```{r}
library(readr)
library(dplyr)
library(ggplot2)
library(tidyr)
library(here)
```

```{r}
lobster_traps <- read_csv(here::here("data/Lobster_Trap_Counts_All_Years_20210519.csv"))
```

```{r}
lobster_traps <- lobster_traps %>% 
    mutate(TRAPS = na_if(TRAPS, -99999))
```

```{r}
unique(lobster_traps)
```

```{r}
not_napl <- lobster_traps %>% 
    filter(SITE != "NAPL")
```

```{r}
carp_20_traps <- lobster_traps %>% 
    filter(SITE == "CARP" & TRAPS > 20)
```

```{r}
# `group_by() %>% summarize()` practice

max_lobster <- lobster_abundance %>% 
  group_by(SITE, MONTH) %>% 
  summarize(MAX_LENGTH = max(SIZE_MM, na.rm = TRUE))
```

<<<<<<< HEAD

=======
## Exercise: Data Visualization

```{r}

## Run this chunk to test exercises ##

library(readr)
library(dplyr)
library(ggplot2)
library(tidyr)


```

```{r}
ggplot(data = lobster_traps, aes(x = TRAPS)) +
    geom_histogram() +
    facet_wrap( ~ YEAR)
```

```{r}
lobsters_traps_summarize <- lobster_traps %>% 
  group_by(SITE, YEAR) %>% 
  summarize(TOTAL_TRAPS = sum(TRAPS, na.rm = TRUE))
```

```{r}
# line plot
ggplot(data = lobsters_traps_summarize, aes(x = YEAR, y = TOTAL_TRAPS)) +
    geom_line(aes(color = SITE))

# line and point plot
ggplot(data = lobsters_traps_summarize, aes(x = YEAR, y = TOTAL_TRAPS)) +
    geom_point(aes(color = SITE)) +
    geom_line(aes(color = SITE))
```


```{r}
p_line <- ggplot(data = lobsters_traps_summarize, aes(x = YEAR, y = TOTAL_TRAPS)) +
    geom_point(aes(color = SITE)) +
    geom_line(aes(color = SITE))

dir.create("figs", showWarnings = FALSE)

ggsave("figs/lobster_line_plot.png", plot = p_line, width = 8, height = 5)
```












```{r}
lobster_traps_fishing_pressure <- lobster_traps %>% 
    filter(YEAR %in% c(2019, 2020, 2021)) %>%
    mutate(FISHING_PRESSURE = if_else(TRAPS >= 8, true = "high", false = "low")) %>%
    group_by(SITE, FISHING_PRESSURE) %>%
    summarize(COUNT = n()) %>%
    drop_na()
```

```{r}
# bar plot
ggplot(data = lobster_traps_fishing_pressure, aes(x = SITE, y = COUNT, fill = FISHING_PRESSURE)) +
    geom_col()

# dodged bar plot
ggplot(data = lobster_traps_fishing_pressure, aes(x = SITE, y = COUNT, fill = FISHING_PRESSURE)) +
    geom_col(position = "dodge")
```

